---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rlolesports

<!-- badges: start -->
<!-- badges: end -->

The goal of rlolesports is to enable easy queries of the unofficial 
Riot Games Esports API for League of Legends. 
It is very much a package in development, not yet tested extensively. 

The package offers very much opinionated data processing of the original
JSON returns of the API. Thus, every user-facing function has a variable 
`save_details`, which can be set to `TRUE` to return the original and unparsed
query result. Without the flag, functions are built to return lists or data.frames
for easy processing in the `dplyr` universe. 

## Installation

You can install the current version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("flsck/rlolesports")
```

## Example

Example is tbd, we'll take a look at the getWindow function later.

```{r example}
library(rlolesports)
## basic example code
```

